Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-31 paper/model.tex
Updated graphical model
updated the abstract -- is it better?
making a sweep through the paper, partial commit

\label{sec:model} We define here a hierarchically supervised LDA
model. Although we will focus on document modeling in our description
and experiments, this model applies equally well to other collections
of discrete data with hierarchically constrained labels.

@@

% generalize to arbitrary codes (not just ICD-9's
%
\begin{figure}[h]
%tbp] %  figure placement: here, top, bottom, or page
 \centering \includegraphics[scale=0.3]{Graphical_Model2} \caption{adapted sLDA model}

@@

\begin{itemize}
\item Draw $a_{l,d}\mid \bar{\mathbf{z}}_d,\boldsymbol\beta_{l},y_{\mathrm{pa}(l),d}\sim\begin{cases}
\mathcal{N}(\bar{\mathbf{z}}^{T}\boldsymbol\beta_{l},1), & y_{\mathrm{pa}(l)}=1\\
\mathcal{N}(\bar{\mathbf{z}}^{T}\boldsymbol\beta_{l},1)\mathbb{I}(a_{l,d}<0), & y_{\mathrm{pa}(l)}=-1\end{cases}$ \\where $\bar{z}_{d}=N_{d}^{-1}\sum_{n=1}^{N}z_{n,d}$ %\item Draw $a_{l, d} \ | \ z_{1:N_d,d}, \boldsymbol\beta_l \sim \mathcal{N} \left(\bar z_d^{T} \boldsymbol\beta_{l},1\right)$, where $\bar z_d=N_d^{-1}\sum_{n=1}^{N_d}z_{n,d}$

>>>>

\label{sec:model} 
%We define here a hierarchically supervised LDA
%model. Although we will focus on document modeling in our description
%and experiments, this model applies equally well to other collections
%of discrete data with hierarchically constrained labels.

HSLDA is a model for hierarchically, multiply labeled, bag-of-words data.  We will refer to the grouped bag-of-word data as a document.  Let $w_{n,d} \in \Sigma$ be the $n$th observation in the $d$th document.  Let $\mathbf{w}_d = \{w_{1,d},\ldots,w_{1,N_d}\}$ be the ordered set of $N_d$ observations in document $d$.  Let there be $D$ such documents and let the size of the vocabulary be $V=|\Sigma|$.

@@

% generalize to arbitrary codes (not just ICD-9's
%
\begin{figure}[t]
%tbp] %  figure placement: here, top, bottom, or page
 \centering \includegraphics[scale=0.4]{Graphical_Model-final} \caption{HSLDA graphical model}

@@

\begin{itemize}
\item Draw $a_{l,d}\mid \bar{\mathbf{z}}_d,\boldsymbol\beta_{l},y_{\mathrm{pa}(l),d}\sim\begin{cases}
\mathcal{N}(\bar{\mathbf{z}}^{T}\boldsymbol\eta_{l},1), & y_{\mathrm{pa}(l)}=1\\
\mathcal{N}(\bar{\mathbf{z}}^{T}\boldsymbol\eta_{l},1)\mathbb{I}(a_{l,d}<0), & y_{\mathrm{pa}(l)}=-1\end{cases}$ \\where $\bar{z}_{d}=N_{d}^{-1}\sum_{n=1}^{N}z_{n,d}$ %\item Draw $a_{l, d} \ | \ z_{1:N_d,d}, \boldsymbol\beta_l \sim \mathcal{N} \left(\bar z_d^{T} \boldsymbol\beta_{l},1\right)$, where $\bar z_d=N_d^{-1}\sum_{n=1}^{N_d}z_{n,d}$
